Le titre

### 2022-08-23 Manuscrit Thèse/chapter 4/Chapter 4.tex
tata

\section{Modification of NV-NV CR in the transverse field dominated regime}
In this part, we will study the cross-relaxation between NV centers whose spin Hamiltonian is dominated by a transverse field, either magnetic or electric. This is an important regime because it corresponds to the low magnetic field region where the electric field dominates, which is the region for which we want to implement our magnetometry protocol. We will also study here the double flip CR processes which we had neglected in the last chapter.

@@

\subsubsection{Change in eigenstates}
The first explanation is the modification of the dipole-dipole interaction caused by the change of the NV Hamiltonian eigenbasis from $\{ \ket{0}, \ket{\pm 1} \}$ when $\mathbf{B} \neq 0$ to $\{ \ket{0}, \ket{\pm} \}$ when $\mathbf{B} = 0$.

@@

The inclusion of double flips in zero field with $\bar{R}^2=0.5$ therefore increases the theoretical  decay rate in zero field by [REF] \% compared to the previous case. 
\subsubsection{Change in $T_2^*$}

@@

We then find that the modification of $T_2^*$ should increase the decay rate in zero field by $\sim 6 \%$ for sample Sumi-2, and by $\sim 19 \%$ for sample CVD-pink. 
\subsection{NV-NV CR under purely transverse magnetic field}

We now want to experimentally discriminate these different contributions and to see how close the actual decay rate is to the theoretical one.

One of the reason we want to discriminate these contributions is that they scale differently with the different variables of the sample ($T_2^*$, $\gamma_f$ , magnetic VS electric noise ...). Understanding which of these effect dominates the zero field dynamics might give us insight on which parameter to optimize if one wants to avoid the zero field depolarization, or on the contrary to increase it.

@@

Instead of an electric field, we will use a transverse magnetic field, which as described in sec. \ref{sec B transverse} leads to a spin Hamiltonian similar to the one where the transverse electric field dominates, or at least to similar eigenstates.

\subsection{Other potential causes}
Alignment : 100 et perp (utiliser la carte)
Pola laser

>>>>

\section{NV-NV CR in the low magnetic field regime}
In this part, we will study the cross-relaxation between NV centers whose spin Hamiltonian is dominated by a transverse field, either magnetic or electric. This is an important regime because it corresponds to the low magnetic field region where the electric field dominates, which is the region for which we want to implement our magnetometry protocol. We will also study here the double flip CR processes which we had neglected in the last chapter.

@@

\subsubsection{Eigenstates modification}
The first explanation is the modification of the dipole-dipole interaction caused by the change of the NV Hamiltonian eigenbasis from $\{ \ket{0}, \ket{\pm 1} \}$ when $\mathbf{B} \neq 0$ to $\{ \ket{0}, \ket{\pm} \}$ when $\mathbf{B} = 0$.

@@

The inclusion of double flips in zero field with $\bar{R}^2=0.5$ therefore increases the theoretical  decay rate in zero field by [REF] \% compared to the previous case. 
\subsubsection{$T_2^*$ modification}

@@

We then find that the modification of $T_2^*$ should increase the decay rate in zero field by $\sim 6 \%$ for sample Sumi-2, and by $\sim 19 \%$ for sample CVD-pink. 
\subsection{Other potential causes}
Alignment : 100 et perp (utiliser la carte)
Pola laser

\section{NV-NV CR under purely transverse magnetic field}
We now want to experimentally discriminate these different contributions and to see how close the actual decay rates are to the predicted ones.

One of the reason we want to separate these contributions is that they scale differently with the different variables of the sample ($T_2^*$, $\gamma_f$ , magnetic VS electric noise ...). Understanding which of these effect dominates the zero field dynamics might give us insight on which parameter to optimize if one wants to avoid the zero field depolarization, or on the contrary to increase it.

@@

Instead of an electric field, we will use a transverse magnetic field, which as described in sec. \ref{sec B transverse} leads to a spin Hamiltonian similar to the one where the transverse electric field dominates, or at least to similar eigenstates.
\subsection{Principle of the experiment}
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{Figures/transis_transverse_field}
\caption{Simulation of the eigenstates of the NV Hamiltonian for $d_\perp E_perp=4\ \rm MHz$ and a purely transverse magnetic field $B_\perp$. (a) Eigenvalues for the spin Hamiltonian as a function of $B_\perp$. The three states are labeled $\ket{1}$, $\ket{2}$ and $\ket{3}$ (b) Splitting between the $\ket{2}$ and $\ket{3}$ states (blue curve) and closeness factor $\abs{\bra{3}\ket{+}}^2$ between the $\ket{3}$ and $\ket{+}$ (red curve)}
\label{eigenstates transverse field}
\end{figure}

Fig. \ref{eigenstates transverse field} shows a simulation of the eigenstates and eigenenergies for a NV Hamiltonian subject to transverse electric field and magnetic field. For convenience we chose to take $E_\perp = E_x$ and $B_\perp = B_x$, taking other geometric configuration only alters slightly the results. We labeled the eigenstates of the Hamiltonian $\ket{1}$, $\ket{2}$ and $\ket{3}$ in ascending order of energy.

Fig. \ref{eigenstates transverse field}-b) shows both the splitting $\Delta \nu$ between the $\ket{2}$ and $\ket{3}$ states, and how close the $\ket{3}$ state is to the $\ket{+}=\frac{\ket{+1}+\ket{-1}}{\sqrt{2}}$ state via the factor $\abs{\bra{3}\ket{+}}^2$. We look at the $\ket{3}$ state since $\ket{2}=\ket{-}=\frac{\ket{+1}-\ket{-1}}{\sqrt{2}}$ in this case.

These two metrics, $\Delta \nu$ and $\abs{\bra{3}\ket{+}}^2$ are what we are interested in: we want to increase $\Delta \nu$ to the point where the double flips are completely quenched, but we want $\abs{\bra{3}\ket{+}}^2$ to remain close to 1 since we wanted to observe the modification caused by the eigenbasis $\{\ket{0},\ket{\pm}\}$. This way we can isolate the $T_1^{\rm dd}$ contribution coming from the change of eigenstates to the one coming from the double flips. Based on the plots in Fig.\ref{eigenstates transverse field}-b), the region with $B_\perp \in$ [100,200] G seems to satisfy both these criteria.
